---
title: "J.Kimbrough_DATA-413_WebscrapingHW"
output:
  pdf_document: default
  html_document: default
date: "2024-11-12"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading Libraries

```{r}
library(rvest)
library(dplyr)
library(tidyverse)
```

## establishing html

```{r}
#establishing html
html <- read_html("https://www.american.edu/cas/mathstat/faculty/index.cfm#all-math-fac")
html
```

# ---Web Scraping---

## scraping the full-time faculty & staff NAMES

```{r}
# scraping the full-time faculty & staff NAMES
staff_names <- html %>% html_nodes(".profile-name span") %>%
  html_text()
staff_names
```


## scraping the full-time faculty & staff POSITIONS

```{r}
# scraping the full-time faculty & staff POSITIONS
staff_positions <- html %>% html_nodes("span+ small") %>% html_text()
staff_positions
```


## scraping the full-time faculty & staff EMAILS (if given)

```{r}
# scraping the full-time faculty & staff EMAILS (if given)
## one staff member listed does NOT have an email
staff_email_raw <- html %>% html_nodes(".profile-email span") %>% html_text()
staff_email_raw
```


## scraping the full-time faculty & staff PHONE #s (if given)

```{r}
# scraping the full-time faculty & staff PHONE #s (if given)
## every staff member listed does NOT have a number
staff_phone_raw <- html %>% html_nodes(".profile-phone span") %>% html_text()
staff_phone_raw
```


# ---Cleaning Data---

## staff member with NO email

```{r}
# staff member with NO email
no_email_staff <- c("Nimai Mehta")
```


## staff members with NO phone number

```{r}
# distinguishing which staff member did NOT have a number
no_phone_staff <- c("Zois Boukouvalas", 
                         "Andrea Correll", 
                         "James Dickens", 
                         "David Gerard", 
                         "William Howell", 
                         "Zeynep Kacar", 
                         "Chris Mitchell", 
                         "Rebecca Steiner", 
                         "Zeying Wang", 
                         "Whiting Wicker")
```


## empty vectors for emails and phone numbers

```{r}
# initialize empty vector to store all emails
## keeps the same length as `staff_names`
staff_email <- vector("character", length(staff_names))


# initialize empty vector to store all phone numbers
## keeps the same length as `staff_names`
staff_phone <- vector("character", length(staff_names))
```


## for loop for emails

```{r}
# assigns NA or the correct email to each staff/faculty
email_index <- 1 #(to track the current position in the `staff_email_raw` list)
for (i in seq_along(staff_names)) {
  if (staff_names[i] %in% no_email_staff) 
    {
    # (will set email to NA if the staff/faculty is in the `no_email_staff` list)
    staff_email[i] <- NA
    } else {
    # (assign the next available email from the list)
    staff_email[i] <- staff_email_raw[email_index]
    email_index <- email_index + 1  # (moves to the next email)
    }
}
```


## for loop for phone numbers

```{r}
# loop over each name to assign phone numbers correctly
phone_index <- 1  # (tracks the current position in the `staff_phone_raw` list)
for (i in seq_along(staff_names)) {
  if (staff_names[i] %in% no_phone_staff) 
    {
    # (will set phone # to NA for staff/faculty without a phone number in the `no_phone_staff` list)
    staff_phone[i] <- NA
    } else {
    # (assigns the next available phone number [hopefully keeping the right order])
    staff_phone[i] <- staff_phone_raw[phone_index]
    phone_index <- phone_index + 1  # (moves to the next phone number)
    }
}

```


# ---Creating Data & CSV---

## create the final data frame

```{r}
# create the final data frame
au_math_stat_dep_staff <- data.frame(
  staff_names,
  staff_positions,
  staff_email,
  staff_phone,
  stringsAsFactors = FALSE #(will keep my data as characters rather than make them factors)
)
```


## view the data before making it csv

```{r}
# view the data before making it csv [making sure it's right like on the html page]
view(au_math_stat_dep_staff)
```


## make the csv

```{r}
# make the csv
write.csv(au_math_stat_dep_staff, "J.Kimbrough_DATA-413_AUMathDepartmentFaculty.csv")
```

