---
title: "J.Kimbrough_DATA-413_AsynchronousSQL"
output:
  pdf_document: default
  html_document: default
date: "2024-10-10"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r pressure, echo=FALSE, message=FALSE}
library(DBI)
library(duckdb)
library(nycflights13)
library(tidyverse)
```

```{r}
con <- dbConnect(duckdb(dbdir = "C:/Users/jkimb/OneDrive/Desktop/School/Classes/VI. Fall 2024/MTh_DATA-413_Data Science/Data/flights.duckdb", read_only = TRUE))
```


# Practice 1: Select Flights from a Specific Carrier
## Write a SQL query to find all flights from the carrier "United Air Lines Inc.".

```{sql, connection=con}

SELECT *
FROM flights
WHERE carrier = 'UA';

```

### I Solved the Practice 1 and you must do the rest. 
## ------------------------------------------------------------------------------------------------------

# Practice 2: Count the Number of Flights for Each Carrier 
## Write a SQL query to count the total number of flights for each carrier.

```{sql, connection=con}

SELECT carrier, COUNT (*) AS total_flights
FROM flights
GROUP BY carrier;

```

## ------------------------------------------------------------------------------------------------------

# Practice 3: Find the Flights with the Longest Distance
## Write a SQL query to find the 10 longest flights based on the distance column.

```{sql, connection=con}

SELECT * 
FROM flights
ORDER BY distance DESC
LIMIT 10;

```

## ------------------------------------------------------------------------------------------------------


# Practice 4: Calculate Average Arrival Delay for Each Carrier
## Write a SQL query to calculate the average arrival delay (arr_delay) for each carrier, showing only those with a non-null delay.

```{sql, connection=con}

SELECT carrier, AVG(arr_delay) AS avg_arrival_delay
FROM flights
WHERE arr_delay IS NOT NULL
GROUP BY carrier;

```

## ------------------------------------------------------------------------------------------------------

# Practice 5: Find Flights Departing from JFK to LAX
## Write a SQL query to find all flights departing from JFK airport to LAX airport.

```{sql, connection=con}

SELECT *
FROM flights
WHERE origin = 'JFK' AND dest = 'LAX';

```

## ------------------------------------------------------------------------------------------------------

# Practice 6: Calculate the Total Number of Flights Each Month
## Write a SQL query to count the total number of flights for each month.

```{sql, connection=con}

SELECT month, COUNT(*) AS total_flights
FROM flights
GROUP BY month
ORDER BY month;

```


## ------------------------------------------------------------------------------------------------------


# Practice 7: Find Flights with Departure Delays Greater than 2 Hours
## Write a SQL query to find all flights that had a departure delay of more than 120 minutes.

```{sql, connection=con}

SELECT * 
FROM flights
WHERE dep_delay > 120; 

```

## ------------------------------------------------------------------------------------------------------

# Practice 8: Find the Number of Flights per Day
## Write a SQL query to count the number of flights for each day (use year, month, and day columns).

```{sql, connection=con}

SELECT "year", "month", "day", COUNT(*) AS flights_per_day
FROM flights
GROUP BY "year", "month", "day"
ORDER BY "year", "month", "day";


```


## ------------------------------------------------------------------------------------------------------
# Practice 9: Find Flights That Arrived Early
## Write a SQL query to find all flights that arrived early (i.e., arr_delay is negative).

```{sql, connection=con}

SELECT *
FROM flights
WHERE arr_delay < 0;

```

## ------------------------------------------------------------------------------------------------------

# Practice 10: Find the Average Air Time per Carrier
## Write a SQL query to find the average air time for each carrier.

```{sql, connection=con}

SELECT carrier, AVG(air_time) AS avg_air_time
FROM flights
GROUP BY carrier;

```

## ------------------------------------------------------------------------------------------------------