---
title: "J.Kimbrough_DATA-413_HW2"
output: pdf_document
date: "2024-10-02"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r pressure, echo=FALSE, message=FALSE}
library(tidyverse)
```

# Problem 1: 
```{r}
library(tidyverse)
tribble( ~x,     ~y,   ~w,    ~z, 
         210,    300,  220,   180, 
         102,    100,  119,   187, 
         176,    175,  188,   173, 
         87,     95,   91,    94, 
         202,    210,  234,   218, 
         110,    122,  131,   128,
) -> dt
dt
```

## 1a.
### Use and show a map function to find the "mean" of each column of the dt data table. 
```{r}
column_means <- dt %>% 
  map_dbl(mean)
column_means
```

## 1b.
### Use and show a map function that will calculate the "standard deviation" of each value of each column of the data table dt. 
```{r}
column_sds <- dt %>% 
  map_dbl(sd)
column_sds
```

## 1c. 
### Use and show a map function that will calculate the "square root" of each value of each column of the data table dt.
```{r}
column_sqrts <- dt %>% 
  map_df(sqrt)
column_sqrts
```

## 1d.
### Use R code to find the "mean", "max", "1st Quartile", "3rd Quartile", "Median", and "Min" for each column of the dt data table. (Hint: You do not have to use a map function).
```{r}
column_summaries <- dt %>% 
  summary()
column_summaries
```
# ------------------------------------------------------------------------------

# Problem 2:

### Write a function that uses a for loop for each iteration, randomly draws 5 observations from an exponential distribution with "rate" parameter 1 (use rexp()) and calculates its "mean". It should do this 10,000 times. Choose an appropriate plot to plot the distribution of "means". 

```{r}
set.seed(123)

draw_means_for <- function(iterations = 10000, sample_size = 5, rate = 1){
  means <- numeric(iterations)
  
  for(i in 1:iterations){
  sample <- rexp(sample_size, rate)
  means[i] <- mean(sample)
  }
  return (means)
}

means_for <- draw_means_for()

```

```{r}
means_df <- data.frame(means = means_for)

ggplot(means_df, aes(x = means)) +
  geom_histogram(fill = "blue", color = "black") +
  xlab("Mean") + 
  ggtitle("Distribution of Means (For Loop)")
```



## 2a.
### Repeat part 1 by using a map_* () function. 
```{r}
set.seed(123)

means_map <- map_dbl(1:10000, ~ mean(rexp(5, rate = 1)))
```

```{r}
means_map_df <- data.frame(means = means_map)

ggplot(means_map_df, aes(x = means)) +
  geom_histogram(fill = "blue", color = "black") +
  xlab("Mean") + 
  ggtitle("Distribution of Means (map_dbl)")
```


## 2b. 
### Repeat part 1 by using the replicate () function.
```{r}
set.seed(123)

means_replicate <- replicate(10000, mean(rexp(5, rate = 1)))
```

```{r}
means_replicate_df <- data.frame(means = means_replicate)

ggplot(means_replicate_df, aes(x = means)) +
  geom_histogram(fill = "blue", color = "black") +
  xlab("Mean") + 
  ggtitle("Distribution of Means (replicate)")
```


## 2c.
### Use another for loop that will print out plots for sample size of 5, 10, and 20 observations (instead of just 5).
```{r}
sample_sizes <- c(5, 10, 20)

set.seed(123)

for(n in sample_sizes){
  means <- numeric(10000)
  
  for(i in 1:10000){
    sample <- rexp(n, rate = 1)
    means[i] <- mean(sample)
  }
  hist(means, main = paste("Distribution of Means (Sample Size:", n, ")"),
       xlab = "Mean", breaks = 30) 
}


#helpful link: https://www.geeksforgeeks.org/histograms-in-r-language/
```


# ------------------------------------------------------------------------------

# Problem 3: 
### Use and show R coding to calculate the "standard deviation" for each variable of the data table mtcars using the "Special For Loop Method".

```{r}
data("mtcars") 
mtcars 
```

```{r}
output <- vector("double", ncol(mtcars))
for(i in seq_along(mtcars)){
  output[[i]] <- sd(mtcars[[i]])
}
names(output) <- colnames(mtcars)

output
```

